Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-23 paper.tex
cast for UD

Hypercoercions for the UD blame tracking strategy have the same syntax
as for D (\figref{fig:hypercoercion}), but the definitions of $id$,
$cast$, and $seq$, given Figure~\ref{fig:HC-UD}, differ from D.
Again, the $seq$ operator is defined in terms of composition, but here
composition $c_1 \fatsemi c_2$ makes the usual assumption that the
target type of $c_1$ matches the source type of $c_2$.  The definition
of composition for UD is particularly straightfoward. The first two
lines say that $\hyperCoercionI$ acts as the identity on both the left
and right. The third line handles the case when both the tail of $c_1$
and the head of $c_2$ are no-ops, in which case the middles types
$m_1$ and $m_2$ are composed via an auxiliary composition
operator. This compose operator for middle coercions assumes that its
inputs are shallowly consistent.  The fourth line handles the
important case when the tail of $c_1$ is an injection and the head of
$c_2$ is a projection. If the two middle coercions are shallowly
consistent, then they can be composed. If not, the tail of the result
is a failure coercion with the projection's label.  The last line
handles the case when the tail of $c_1$ is a failure, in which case
the result of composition is $c_1$.

@@

  \caption{Lazy UD Hypercoercions}
  \label{fig:HC-UD}
\end{figure}

Figure~\ref{fig:HC-UD-cast}

@@

\todo[inline]{talk about $cast(T,l,T)$. -JS}

>>>>

Hypercoercions for the UD blame tracking strategy have the same syntax
as for D (\figref{fig:hypercoercion}), but the definitions of $id$,
$cast$, and $seq$, differ from D.  Again, the $seq$ operator
(Figure~\ref{fig:HC-UD}) is defined in terms of composition, but here
composition $c_1 \fatsemi c_2$ makes the usual assumption that the
target type of $c_1$ matches the source type of $c_2$.  The definition
of composition for UD is particularly straightfoward. The first two
lines say that $\hyperCoercionI$ acts as the identity on both the left
and right. The third line handles the case when both the tail of $c_1$
and the head of $c_2$ are no-ops, in which case the middles types
$m_1$ and $m_2$ are composed via an auxiliary composition
operator. This compose operator for middle coercions assumes that its
inputs are shallowly consistent.  The fourth line handles the
important case when the tail of $c_1$ is an injection and the head of
$c_2$ is a projection. If the two middle coercions are shallowly
consistent, then they can be composed. If not, the tail of the result
is a failure coercion with the projection's label.  The last line
handles the case when the tail of $c_1$ is a failure, in which case
the result of composition is $c_1$.

The definition of $id$ is straightforward (Figure~\ref{fig:HC-UD}) .

@@

  \fbox{$id( T ) = c$}
  \[
  \begin{array}{rclr}
    \funrule{id(\star)}{
    \hyperCoercionI
    }{}
    \funrule{id(P)}{
    \hyperCoercionC{\epsilon}{id(P)}{\epsilon}
    }{}
  \end{array}
  \]
  \caption{Lazy UD Hypercoercions}
  \label{fig:HC-UD}
\end{figure}

@@

The $cast$ function is defined in Figure~\ref{fig:HC-UD-cast}.  Prior
presentations of this function do not use auxiliary functions, as we
do here. The reason that we introduction the auxiliary functions
$\mathit{castToDyn}$, $\mathit{castFromDyn}$, $\mathit{castToInj}$,
and $\mathit{castFromInj}$, is to ensure that all of the are
structurally recursive, which makes them straightforward to define in
Agda.
